Double check some data and calculate some summaries for the text
========================================================
First load in the data.   
```{r load-data}
setwd("~/BitBucket/VIT2014/Analysis")
rm(list = ls())
library(knitr)
library(lubridate)
Data <- read.table("VIT_Data2014.txt", sep="", header=T) #load in data

# reformat some of the dates
Data$CaptureDate<- mdy(as.character(Data$CaptureDate))
Data$Start_Interval <- mdy(as.character(Data$Start_Interval))
Data$Stop_Interval <- mdy(as.character(Data$Stop_Interval))
                       
# insert death dates on mothers that died
Data$Stop_Interval[Data$VIT_Status == "Died"] <- Data$Start_Interval[Data$VIT_Status == "Died"]
Data$CapDOY <- yday(Data$CaptureDate) # day of the capture (1-365)
Data$StartDOY <- yday(Data$Start_Interval) # day when the VIT is first possibly out
Data$EndDOY <- yday(Data$Stop_Interval) # last day the event (birth or abortion) could have happened
```

Total # of elk in the original dataset = `r dim(Data)[1]`. 
  
```{r subset}
# first remove the individuals that were not pregnant or were unknown events. 
Data <- subset(Data, Data$VIT_Status != "Open" )
Data <- subset(Data, Data$VIT_Status != "Unknown" )
Data$VIT_Status <- as.factor(as.character(Data$VIT_Status)) #relevel the factor

DataPOS <- Data[Data$CowSero == "POS", ]

days <- seq(min(Data$CapDOY), max(Data$EndDOY))
```

Total # of elk in the analyzed dataset = `r dim(Data)[1]`.  
Total # of seropositive elk in the analyzed dataset = `r dim(DataPOS)[1]`. 
  
Table of Abortions by mothers status:  
```{r table1, echo=FALSE}
(table1 <- table(Data$CowSero, Data$VIT_Status))
```
  
The chance of aborting, given survival and seronegative =   
```{r binom-neg}
binom.test(table1[1,1], sum(table1[1,c(1,3)]))
```
  
And for the seropositives: 
```{r binom-pos}
binom.test(table1[2,1], sum(table1[2,c(1,3)]))
```
  
The first abortion was between 
```{r 1st-abort, echo=FALSE}
first_ab_beg <- Data$Start_Interval[Data$VIT_Status == "Abortion"]
last_ab_beg <- sort(yday(first_ab_beg), decreasing = T)[1]
first_ab_beg <- sort(yday(first_ab_beg))[1]

first_ab_end <- Data$Stop_Interval[Data$VIT_Status == "Abortion"]
last_ab_end <- sort(yday(first_ab_end), decreasing = T)[1]
first_ab_end <- sort(yday(first_ab_end))[1]
```
`r as.Date("2013/01/01")+first_ab_beg` and `r as.Date("2013/01/01")+first_ab_end`, and the last abortion was between `r as.Date("2013/01/01")+last_ab_beg` and `r as.Date("2013/01/01")+ last_ab_end`. Note: ignore the year here, just use the day of the year. 

  
Plot the sampling intensity over day of year.  
```{r plot-intensity, echo = F}
# calculate the # online per day
N <- rep(NA, length(days))
for (i in 1:length(days)){
  d <- days[i]
  tmp <- subset(Data, Data$CapDOY <= d & Data$EndDOY > d)
  if(is.null(tmp) == T){N[i] <- 0}
  if(is.null(tmp) == F){N[i] <- dim(tmp)[1]}
}
Npos <- rep(NA, length(days))
for (i in 1:length(days)){
  d <- days[i]
  tmp <- subset(DataPOS, DataPOS$CapDOY <= d & DataPOS$EndDOY > d)
  if(is.null(tmp) == T){Npos[i] <- 0}
  if(is.null(tmp) == F){Npos[i] <- dim(tmp)[1]}
}

ab_all <- subset(Data, Data$VIT_Status == "Abortion")
ab_pos <- subset(DataPOS, DataPOS$VIT_Status == "Abortion")
t <- as.Date('01/01/2013', '%d/%m/%Y') + days 
  
plot(t, N, type = 'l', xlab = '')
lines(t, Npos, type = 'l', col = 'red')
points(as.Date('01/01/2013', '%d/%m/%Y') + yday(ab_all$Stop_Interval), 
       rep(400, dim(ab_all)[1]))
points(as.Date('01/01/2013', '%d/%m/%Y') + yday(ab_pos$Stop_Interval), 
       rep(0, dim(ab_pos)[1]))
```

