---
output: html_document
---
Figure Legends
=====================================================
```{r setup, echo = FALSE}
library(knitr)
opts_chunk$set(dev=c('png'), dpi = 400, echo = FALSE, message = FALSE, cache = F, fig.cap= "", fig.lp="")
setwd("~/BitBucket/VIT2014/Analysis")
```

**Figure 1.** Probable abortion and live birth locations from elk with vaginal implant transmitters in the southern region of the Greater Yellowstone Ecosystem. 
    
**Figure 2**. Timelines of brucellosis seropositive elk reproductive events from the vaginal implant transmitters (VITs, A) and a histogram of opportunisitically recovered fetuses on feedgrounds from 1968 to 2014 (B). In A, grey lines extend from the capture date to the time interval of the reproductive event. Red and blue lines indicate time intervals when VITs were expelled due to abortions or normal birth events, respectively. 

**Figure 3**. Daily hazard of an abortion for female elk exposed to *Brucella abortus* given she is still pregnant using the 40-knot spline model. Live births were either censored (A) or included in the full model where the total hazard was partitioned between two cause-specific event types (B, abortions and live births). Grey and black solid lines are the posterior mean and medians, respectively. Dotted lines are the posterior 95% credible intervals.   
    
**Figure 4**. The probability that a reproductive event was an abortion using the full 40-knot spline model. Grey and black solid lines are the posterior mean and medians, respectively. Dotted lines are the posterior 95% credible intervals. 

**Figure 5**. Seasonal elk reproductive event hazards (A and C) and event densities (B and D) estimated from the full 40-knot spline model. Hazards are conditional on the elk still being pregnant. Grey and black solid lines are the posterior mean and medians, respectively. Dotted lines are the posterior 95% credible intervals.

\newpage  

Figures
=====================================================

![Fig1][1]  
\newpage

```{r Fig2, fig.width = 3.34, fig.height = 5}
rm(list = ls())
library(lubridate)
load('VIT_Data2014_Full_POS.RData')
source('VITplot_interval2.R')

par(mfrow = c(2,1), mar = c(2,3,0.25,0.25), cex = 1, mgp = c(1.5,.25,0))
#Figure 2A
VITplot_interval2(DataPOS, 2) 
text(as.Date("2013/01/01"), 130, "A)", pos = 4, cex = 1)

#Figure 2B: Fetus recovery data
Fetus <- read.table('FetusRecoveryField.txt', header = T) #read in data
Fetus$Date2 <- mdy(Fetus$Date) # reformat dates
Fetus$DOY <- yday(Fetus$Date2) # reformat dates
Fetus <- Fetus[order(Fetus$DOY),] # sort by doy
Fetus <- subset(Fetus, is.na(Fetus$Date2) == F) # remove the NAs

# PLOT
hist(Fetus$DOY, breaks = 10, ylim = c(0,14), xlim = c(1, max(DataPOS$EndDOY)), main = '', xlab = "", xaxt = "n", col = 'grey', 
     ylab = "Number of fetuses", tck = 0.02)
axis(1, at = c( 1, 32, 60, 91, 121, 152, 182), 
     labels = c("Jan 1", "Feb 1", "Mar 1", "Apr 1", "May 1", "Jun 1", "Jul 1"), tck = 0.02)
text(1, 13, "B)", pos = 4, cex = 1)
```
    
\newpage  

```{r Fig3, fig.width = 3.34, fig.height = 6}
source('plot_VITresults_fxns.R')
load('Result_mod40k_bcen1.RData')
load('VIT_Data2014_BirthsCensored.RData')

#Part A
start.offset <- min(Data$CapDOY)
par(mfrow = c(2,1), mar = c(2,3,0.5,0.5), mgp = c(1.5,.25,0))
plot_baseline(mod40k_bcen, MainLab = " ", start.offset, 2, Ylim = c(0,0.008), 
            Xlim = as.Date(c('2013/01/15', '2013/07/01')), 
            legendflag=FALSE, FmoTix = T, 
            Ylab = expression(paste("Abortion hazard  ", italic(f)(italic(t)))))
text(as.Date("2013/01/11"), 0.008, "A) Censoring births", pos = 4, cex = 1)

load('Result_mod40k1.RData')
#Part B
plot_hazAb(mod40k, MainLab = " ", start.offset, 2,  Ylim = c(0,0.008), 
           Xlim = as.Date(c('2013/01/15', '2013/07/01')), legendflag=FALSE,
           Ylab = expression(paste("Abortion hazard  ", italic(f)[c==1](italic(t)))),
           FmoTixs = T)
text(as.Date("2013/01/11"), 0.008, "B) Full model", pos = 4, cex = 1)
```

\newpage  

```{r Fig4, fig.width = 3.34, fig.height = 2.5}
par(mfrow = c(1,1), mar = c(2,3,0.25,0.25), cex = 1, mgp = c(1.5,.25,0))
plot_Pabort(mod40k, "", start.offset, 2,  Xlim = as.Date(c('2013/01/15', 
                                                           '2013/07/01')),
            legendflag=FALSE)
```

\newpage  

```{r Fig5, fig.height = 8, fig.width = 7.08}
rm(list = ls())
source('plot_VITresults_fxns.R')
load('Result_mod40k1.RData')
load('VIT_Data2014_Full_POS.RData')
start.offset <- min(Data$CapDOY)

par(mfrow = c(2,2), mar = c(2,3.2,1,1), cex = 1, mgp = c(2,.5,0))
#Top row
plot_hazAb(mod40k, "", start.offset, 2, Ylim = c(0, 0.008), 
          Ylab = expression(paste("Abortion hazard  ", 
                                  italic(h)[c==1](italic(t)))),
          Xlim = as.Date(c('2013/01/15', '2013/07/01')), 
           legendflag=FALSE, FmoTixs = T)
text(as.Date("2013/01/11"), 0.008, "A)", pos = 4, cex = 1)

plot_abort_ft(mod40k, "", start.offset, 2, Ylim = c(0, 0.008), 
           Ylab = expression(paste("Abortion density  ",
                                   italic(f)[c==1](italic(t)))),
           Xlim = as.Date(c('2013/01/15', '2013/07/01')), 
              legendflag=FALSE, FmoTixs = T)
text(as.Date("2013/01/11"), 0.008, "B)", pos = 4, cex = 1)

#Bottom row
plot_hazLB(mod40k, "", start.offset, 2, Ylim = c(0, 0.15),   
           Xlim = as.Date(c('2013/01/15', '2013/07/01')), 
           Ylab = expression(paste("Birth hazard  ", 
                                   italic(h)[c==2](italic(t)))),
           legendflag=FALSE, FmoTixs = T)
text(as.Date("2013/01/11"), 0.15, "C)", pos = 4, cex = 1)
plot_birth_ft(mod40k, "", start.offset, 2, Ylim = c(0, 0.04),  
           Xlim = as.Date(c('2013/01/15', '2013/07/01')),
           Ylab = expression(paste("Birth density  ", 
                                   italic(f)[c==2](italic(t)))),
           legendflag=FALSE, FmoTixs = T)
text(as.Date("2013/01/11"), 0.04, "D)", pos = 4, cex = 1)

```
\newpage  

[1]: figure/Fig1.png
  
