Logistic regressions on probability of abortion vs. birth
========================================================
Doing some initial *easier* models of the probability of abortion vs. birth.  Doing this so that I don't have to do a ton of different MCMC models. 

```{r setup, echo = FALSE}
opts_chunk$set(dev = c('png', 'pdf'), dpi = 500, fig.height = 4, fig.width = 6, echo = FALSE)
# Change the dpi to 96 if only going the html
# Change the dpi to >400 if going to a docx or pdf

```

```{r load-data}
setwd("~/BitBucket/VIT/Analysis")
rm(list = ls())
load('VIT_Data2013_Full.RData')

Type$abort <- 1
Type$abort[Type$VIT_Status == "Parturition"]<- 0
summary(Type)
table(Type$CowSero, Type$VIT_Status)
Type <- subset(Type, is.na(Type$CowSero) == F)
```

For simplicity we'll just assume that all events occur at the end of the interval
```{r models}
model0 <- glm(abort ~ right, data = Type, family = "binomial")
summary(model0)

model1 <- glm(abort ~ right + CowSero, data = Type, family = "binomial")
summary(model1)

model2 <- glm(abort ~ right + CowSero + right*CowSero, data = Type, family = "binomial")
summary(model2)

model3 <- glm(abort ~ CowSero, data = Type, family = "binomial")
summary(model3)

AIC(model0, model1, model2, model3)
```
This is interesting.  Seropositives are more likely to abort, but once you account for the timing, you may not need that variable. 

```{r plot-model1}
Type$pr <- predict(model1, type = "response")
# make fxn to plot the results
plot_logit_rug <- function(data){
  par(mfrow = c(1,1))
  plot(data$right[data$CowSero == "POS"], data$pr[data$CowSero == "POS"], col = 'red', 
       xlab = "Day", ylab = "prob of abortion")
  points(data$right[data$CowSero == "NEG"], data$pr[Type$CowSero == "NEG"], col =  'blue')
  rug(data$right[data$CowSero == "NEG" & data$abort == 0], side = 1, col = 'blue')
  rug(data$right[data$CowSero == "NEG" & data$abort == 1], side = 3, col = 'blue')
  rug(data$right[data$CowSero == "POS" & data$abort == 1], side = 3, col = 'red')
  rug(data$right[data$CowSero == "POS" & data$abort == 0], side = 1, col = 'red')
}

plot_logit_rug(Type)
```

```{r plot-model0}
Type$pr <- predict(model0, type = "response")
plot_logit_rug(Type)
```

But if you don't have the data on when the event occurred. Then Seropositive status is important: 
```{r model3}
model3 <- glm(abort ~ CowSero, data = Type, family = "binomial")
summary(model3)
tmp <- as.data.frame(predict(model3, type = "response", se.fit = T))[1:2, ]
```
So the probability ofa seropositive aborting is `r round(tmp$fit[2], 2)` plus or minus a SE of `r round(tmp$se.fit[2],2)`. Compared to a seronegative: `r round(tmp$fit[1], 2)` plus or minus a SE of `r round(tmp$se.fit[1],2)`. 

This would be on the order of reducing an 80% birth rate to 74% if the overall prevalence is 30%.  (so not too big). 

Any evidence of a feedground effect?
```{r model4}
model4 <- glm(abort ~ CowSero + Feedground, data = Type, family = "binomial")
summary(model4)
anova(model4)
```
Not really. 