Supplementary Information:
=====================================================

```{r setupSupInfo, echo = FALSE}
library(knitr)
opts_chunk$set(dev = "png", dpi = 400, echo = FALSE, message = FALSE)
```

```{r FigS1, fig.height = 7, fig.width = 5, echo = FALSE, fig.cap= "", fig.lp=""}
rm(list = ls())
setwd("~/BitBucket/VIT2014/Analysis")
library(lubridate)
load('VIT_Data2014_Full.RData')
source('VITplot_interval2.R')
start.offset <- min(Data$CapDOY)
par(mfrow = c(1,1), mar = c(2,3,.25,.25), cex = 1.5, mgp = c(2,.5,0), family = "sans", font = 1)
VITplot_interval2(Data, 2)
```
  
**Figure S1**. Raw data on the reproductive events of all pregnant elk in the study. Grey lines extend from the capture date to the time interval when the reproductive event occurred. Red and blue lines indicate time intervals when VITs were expelled due to abortions or normal birth events, respectively.   

\newpage   
  
```{r FigS2, fig.height = 6, fig.width = 7, echo = FALSE, fig.cap= "", fig.lp=""}
load('Result_mod10k1.RData')
load('Result_mod40k1.RData')
load('Result_icar1.RData')
load('VIT_Data2014_Full_POS.RData')
source('plot_VITresults_fxns.R')
start.offset <- min(Data$CapDOY)

par(mfrow = c(2,3), mar = c(2,3,0.5,.25), cex = 1, mgp = c(2,.5,0), family = "sans", 
    font = 1)
plot_abort_ft(mod10k, "", start.offset, 2, Ylim = c(0, 0.008),
              Xlim = as.Date(c('2013/01/15', '2013/07/01')), legendflag=FALSE, 
              Ylab = expression(paste("Abortion density  ", 
                                      italic(f)[c==1](italic(t)))),
              FmoTixs = T)
text(as.Date("2013/01/11"), 0.008, "A) 10 knots", pos = 4, cex = 1)

plot_abort_ft(mod40k, "", start.offset, 2, Ylim = c(0, 0.008),
              Xlim = as.Date(c('2013/01/15', '2013/07/01')), legendflag=FALSE, 
              Ylab = "", FmoTixs = T)
text(as.Date("2013/01/11"), 0.008, "B) 40 knots", pos = 4, cex = 1)

plot_abort_ft(icarmod, "", start.offset, 2,  Ylim = c(0, 0.008),
              Xlim = as.Date(c('2013/01/15', '2013/07/01')), legendflag=FALSE, 
              Ylab = "", FmoTixs = T)
text(as.Date("2013/01/11"), 0.008, "C) CAR model", pos = 4, cex = 1)

plot_birth_ft(mod10k, "", start.offset, 2,   Ylim = c(0, 0.05),
              Xlim = as.Date(c('2013/01/15', '2013/07/01')), legendflag=FALSE, 
              Ylab = expression(paste("Birth density  ", 
                                      italic(f)[c==2](italic(t)))),
              FmoTixs = T)
text(as.Date("2013/01/11"), 0.05, "D) 10 knots", pos = 4, cex = 1)

plot_birth_ft(mod40k, "", start.offset, 2,   Ylim = c(0, 0.05),
              Xlim = as.Date(c('2013/01/15', '2013/07/01')), legendflag=FALSE, 
              Ylab = "", FmoTixs = T)
text(as.Date("2013/01/11"), 0.05, "E) 40 knots", pos = 4, cex = 1)

plot_birth_ft(icarmod, "", start.offset, 2,  Ylim = c(0, 0.05),
              Xlim = as.Date(c('2013/01/15', '2013/07/01')), legendflag=FALSE, 
              Ylab = "", FmoTixs = T)
text(as.Date("2013/01/11"), 0.05, "F) CAR model", pos = 4, cex = 1)
```
  
**Figure S2**. Comparison of reproductive event densities using different smoothing functions and only seropositive elk. Grey and black solid lines are the predicted posterior mean and medians. Dotted lines are the predicted posterior 95% credible intervals. 
  
\newpage
    
```{r FigS3, fig.height = 6, fig.width = 6, echo = FALSE, fig.cap= "", fig.lp=""}
load('Result_mod40k0.RData')
source('plot_VITresults_fxns.R')
start.offset <- min(Data$CapDOY)

par(mfrow = c(2,2), mar = c(2,3,1,1), cex = 1, mgp = c(2,.5,0), family = "sans",
    font = 1)
#Top row
plot_hazAb(mod40k, "", start.offset, 2, Ylim = c(0, 0.004), 
            Ylab = expression(paste("Abortion hazard  ", 
                                    italic(h)[c==1](italic(t)))),
            Xlim = as.Date(c('2013/01/15', '2013/07/01')), 
           legendflag=FALSE, FmoTixs = T)
text(as.Date("2013/01/11"), 0.004, "A)", pos = 4, cex = 1)

plot_abort_ft(mod40k, "", start.offset, 2, Ylim = c(0, 0.004), 
              Ylab = expression(paste("Abortion density  ", 
                                      italic(f)[c==1](italic(t)))),
              Xlim = as.Date(c('2013/01/15', '2013/07/01')), 
              legendflag=FALSE, FmoTixs = T)
text(as.Date("2013/01/11"), 0.004, "B)", pos = 4, cex = 1)

#Bottom row
plot_hazLB(mod40k, "", start.offset, 2, Ylim = c(0, 0.15),   
           Xlim = as.Date(c('2013/01/15', '2013/07/01')), 
           Ylab = expression(paste("Birth hazard  ", 
                                   italic(h)[c==2](italic(t)))),
           legendflag=FALSE, FmoTixs = T)
text(as.Date("2013/01/11"), 0.15, "C)", pos = 4, cex = 1)

plot_birth_ft(mod40k, "", start.offset, 2, Ylim = c(0, 0.04),  
           Xlim = as.Date(c('2013/01/15', '2013/07/01')), 
           Ylab = expression(paste("Birth density  ", italic(f)[c==2](italic(t)))),
           legendflag=FALSE, FmoTixs = T)
text(as.Date("2013/01/11"), 0.04, "D)", pos = 4, cex = 1)

```
  
**Figure S3**. Results using seropositive and seronegative elk and the 40 knot spline model. Grey and black solid lines are the predicted posterior mean and medians. Dotted lines are the predicted posterior 95% credible intervals.

\newpage

**Table S2**. Comparison of elk abortion timing across models when using all pregnant elk (n = `r length(unique(Data$Elk_ID))`). Models had different smoothing functions for the total hazard of a reproductive event, but the sub-model of the probability of an abortion relative to a live birth was a logistic regression in all cases.        
  
```{r SupInfoCTable, echo = FALSE}
rm(list = ls())
load('Result_icar0.RData')
load('Result_mod40k0.RData')
load('Result_mod10k0.RData')
load('VIT_Data2014_Full.RData')
library(knitr)
library(lubridate)
source('ft_calc_fxn.R')
start.offset <- min(Data$CapDOY)

# Calculating summary statistics on the abortion event density for different models. 
ft_icar <- ft_calc(icarmod)
ft_icarcum <- ft_cum_calc(ft_icar$median)
ft_mod10k <- ft_calc(mod10k)
ft_mod10kcum <- ft_cum_calc(ft_mod10k$median)
ft_mod40k <- ft_calc(mod40k)
ft_mod40kcum <- ft_cum_calc(ft_mod40k$median)
ft_mod10k_5 <- start.offset + ft_mod10kcum$row5 
ft_mod40k_5 <- start.offset + ft_mod40kcum$row5 
ft_icar_5 <- start.offset + ft_icarcum$row5 
ft_mod10k_25 <- start.offset + ft_mod10kcum$row25 
ft_mod40k_25 <- start.offset + ft_mod40kcum$row25 
ft_icar_25 <- start.offset + ft_icarcum$row25 
ft_mod10k_75 <- start.offset + ft_mod10kcum$row75 
ft_mod40k_75 <- start.offset + ft_mod40kcum$row75 
ft_icar_75 <- start.offset + ft_icarcum$row75 
ft_mod10k_95 <- start.offset + ft_mod10kcum$row95 
ft_mod40k_95 <- start.offset + ft_mod40kcum$row95 
ft_icar_95 <- start.offset + ft_icarcum$row95 

tab1 <- round(matrix(data = c(mod10k$BUGSoutput$DIC, mod40k$BUGSoutput$DIC, icarmod$BUGSoutput$DIC, mod10k$BUGSoutput$pD, mod40k$BUGSoutput$pD, icarmod$BUGSoutput$pD), 
               nrow = 3), 1)
tab2 <- matrix(data = c(ft_mod10k_5, ft_mod40k_5, ft_icar_5,  
               ft_mod10k_25, ft_mod40k_25, ft_icar_25,  
               ft_mod10k_75, ft_mod40k_75, ft_icar_75,  
               ft_mod10k_95, ft_mod40k_95, ft_icar_95), nrow = 3)
tab3 <- as.data.frame(cbind( rbind("10 knots", "40 knots", "CAR model"), tab1, tab2))

#convert numeric day to Date
tab3[,4] <- as.Date("01/01/2013", "%m/%d/%Y") + as.numeric(as.character(tab3[,4]))
tab3[,5] <- as.Date("01/01/2013", "%m/%d/%Y") + as.numeric(as.character(tab3[,5]))
tab3[,6] <- as.Date("01/01/2013", "%m/%d/%Y") + as.numeric(as.character(tab3[,6]))
tab3[,7] <- as.Date("01/01/2013", "%m/%d/%Y") + as.numeric(as.character(tab3[,7]))

# Convert these to text day of year
tab3[,4] <- paste(mday(tab3[,4]), month(tab3[,4], label = T), sep = "-")
tab3[,5] <- paste(mday(tab3[,5]), month(tab3[,5], label = T), sep = "-")
tab3[,6] <- paste(mday(tab3[,6]), month(tab3[,6], label = T), sep = "-")
tab3[,7] <- paste(mday(tab3[,7]), month(tab3[,7], label = T), sep = "-")

names(tab3) <- c("Model", "DIC", "pD", "5%", "25%", "75%", "95%")

kable(tab3, format = 'markdown')
```
      
DIC: Deviance information criteria  
pD: Estimate of model complexity  
5-95%: Estimated day of the year when *X*% of the abortions have occurred.  

\newpage  

**Appendix S1:** Model code.  
Hazard spline model that is not partitioned by event type (10knots)
-----------------------------------------------------
  
```
  # Priors
  gamma0  ~ dnorm(0, 1.0E-6)
  sigmab ~ dunif(0,3)
  taub <- pow(sigmab, -2)
  for (l in 1:num.knots){b[l]  ~ dnorm(0,taub)}
    
  # Likelihood for the total hazard
  for (j in 1:records) {
    for (k in left[j]:(right[j]-1)) {
      # unit cumulative hazard
      UCH[j,k] <- exp(gamma0 + mre110[k])
    }   	
    
    SLR[j] <- exp(-sum(UCH[j,left[j]:(right[j]-1)])) # total prob of not having an event 
    
    # Bernoulli draw for "surviving"
    noevent[j] ~ dbern(SLR[j])      
  }

# Calculate the baseline hazard
  for (i in 1:D) {
    Haz_b[i] <- exp(gamma0 + mre110[i]) # baseline hazard
    # Spline part
    mre110[i] <- b[1]*Z[i,1]+b[2]*Z[i,2]+b[3]*Z[i,3]+b[4]*Z[i,4]+b[5]*Z[i,5]+
      b[6]*Z[i,6]+b[7]*Z[i,7]+b[8]*Z[i,8]+b[9]*Z[i,9]+b[10]*Z[i,10]
  }               
```
  
Hazard spline model that is partitioned by event type (10knots)
-----------------------------------------------------
 
```
# Priors
sigmab ~ dunif(0,3)
taub <- pow(sigmab, -2)
gamma0  ~ dnorm(0, 1.0E-6)
beta    ~ dunif(0,2) # slope for the probability of an abortion
alpha   ~ dunif(50, 200) # offset for the transition from abortion to birth
K ~ dunif(0,0.5) # lower asymptote for the prob. of an abortion
for (l in 1:num.knots){b[l]  ~ dnorm(0,taub)}

#Derived parameters
for (i in 1:D) {
  Haz_b[i] <- exp(gamma0 + mre110[i]) # baseline hazard

  mre110[i] <- b[1]*Z[i,1]+b[2]*Z[i,2]+b[3]*Z[i,3]+b[4]*Z[i,4]+b[5]*Z[i,5]+
  b[6]*Z[i,6]+b[7]*Z[i,7]+b[8]*Z[i,8]+b[9]*Z[i,9]+b[10]*Z[i,10]

  prob.ab[i] <-  1 + (K - 1) / (1 + exp(-beta*(i - alpha))) # probability of abortion 
  Haz_a[i] <- prob.ab[i] * Haz_b[i]     # abortion hazard
  Haz_l[i] <- (1-prob.ab[i]) * Haz_b[i] # live birth hazard
}               

# Likelihood for the total hazard
for (j in 1:records) {
  for (k in left[j]:(right[j]-1)) {UCH[j,k] <- exp(gamma0 + mre110[k])}   	
    SLR[j] <- exp(-sum(UCH[j,left[j]:(right[j]-1)])) # total prob of not having an event 
    noevent[j] ~ dbern(SLR[j])      
}

# Likelihood on partitioning the event types
for (m in 1:n.events) {
  b.type[m] ~ dbern(p.a[m])
  p.a[m] <- 1 + (K - 1) / (1 + exp(-beta*(event.day[m] - alpha)))
}  
```
  
Estimating the design matrix *Z* for the splines was done in R as follows:   
  
```
Z_K<-(abs(outer(covariate,knots,"-")))^3  
OMEGA_all<-(abs(outer(knots,knots,"-")))^3  
svd.OMEGA_all<-svd(OMEGA_all)  
sqrt.OMEGA_all<-t(svd.OMEGA_all$v %*%  
(t(svd.OMEGA_all$u)*sqrt(svd.OMEGA_all$d)))  
Z<-t(solve(sqrt.OMEGA_all,t(Z_K)))  
```
  
Conditional autoregressive model with event-type partitioning
-----------------------------------------------------
```
  # Priors
  gamma0  ~ dnorm(0, 1.0E-6)
  beta    ~ dunif(0,2) # slope for the probability of an abortion
  alpha   ~ dunif(50, 200) # offset for the transition from abortion to birth
  K ~ dunif(0,0.5) # lower asymptote for the prob. of an abortion
  sd.rho ~ dunif(0,10)  # hyperprior
  tau.rho <- pow(sd.rho, -2)  
  rho[1] ~ dnorm(0, 1.0E-6)
  for (i in 2:D) {rho[i]~dnorm(rho[i-1],tau.rho)}
    
  #Derived quantities
  for (i in 1:D) {
    Haz_b[i] <- exp(gamma0 + rho[i]) # overall baseline
    prob.ab[i] <-  1 + (K - 1) / (1 + exp(-beta*(i - alpha))) # probability of abortion 
    Haz_a[i] <- prob.ab[i] * Haz_b[i]     # abortion hazard
    Haz_l[i] <- (1-prob.ab[i]) * Haz_b[i] # live birth hazard
  }     

  # Likelihood
  for (j in 1:records) {
    for (k in left[j]:(right[j]-1)) {
      UCH[j,k] <- exp(gamma0 + rho[k]) # unit hazard over the interval
    }     
    SLR[j] <- exp(-sum(UCH[j,left[j]:(right[j]-1)]))# total prob of not having an event 
    noevent[j] ~ dbern(SLR[j])      
  }
  
  # Likelihood on partitioning the event types
  for (m in 1:n.events) {
    b.type[m] ~ dbern(p.a[m])
    p.a[m] <- 1 + (K - 1) / (1 + exp(-beta*(event.day[m] - alpha)))
  }  
  
```
