---
output: pdf_document
---
**Table 1**. Comparison of elk abortion timing across models with different smoothing functions for the total hazard of a reproductive event. In all cases, the sub-model of the probability of an abortion relative to a live birth was a logistic regression.        

```{r Table1-comp, echo = FALSE}
setwd("~/BitBucket/VIT2014/Analysis")
load('Result_icar1.RData')
load('Result_mod10k1.RData')
load('Result_mod40k1.RData')
load('VIT_Data2014_Full_POS.RData')
library(knitr)
library(lubridate)
source('ft_calc_fxn.R')
start.offset <- min(Data$CapDOY)

# Calculating summary statistics on the abortion event density for different models. 
ft_icar <- ft_calc(icarmod)
ft_icarcum <- ft_cum_calc(ft_icar$mean)
ft_mod10k <- ft_calc(mod10k)
ft_mod10kcum <- ft_cum_calc(ft_mod10k$mean)
ft_mod40k <- ft_calc(mod40k)
ft_mod40kcum <- ft_cum_calc(ft_mod40k$mean)
ft_mod10k_5 <- start.offset + ft_mod10kcum$row5 
ft_mod40k_5 <- start.offset + ft_mod40kcum$row5 
ft_icar_5 <- start.offset + ft_icarcum$row5 
ft_mod10k_25 <- start.offset + ft_mod10kcum$row25 
ft_mod40k_25 <- start.offset + ft_mod40kcum$row25 
ft_icar_25 <- start.offset + ft_icarcum$row25 
ft_mod10k_75 <- start.offset + ft_mod10kcum$row75 
ft_mod40k_75 <- start.offset + ft_mod40kcum$row75 
ft_icar_75 <- start.offset + ft_icarcum$row75 
ft_mod10k_95 <- start.offset + ft_mod10kcum$row95 
ft_mod40k_95 <- start.offset + ft_mod40kcum$row95 
ft_icar_95 <- start.offset + ft_icarcum$row95 

# model summaries
tab1 <- round(matrix(data = c(mod10k$BUGSoutput$DIC, mod40k$BUGSoutput$DIC, 
                              icarmod$BUGSoutput$DIC, mod10k$BUGSoutput$pD,
                              mod40k$BUGSoutput$pD, icarmod$BUGSoutput$pD), 
               nrow = 3), 1)
# Density estimates
tab2 <- matrix(data = c(ft_mod10k_5, ft_mod40k_5, ft_icar_5,  
               ft_mod10k_25, ft_mod40k_25, ft_icar_25,  
               ft_mod10k_75, ft_mod40k_75, ft_icar_75,  
               ft_mod10k_95, ft_mod40k_95, ft_icar_95), nrow = 3)

# Model names combined with tab1 and tab2
tab3 <- as.data.frame(cbind(rbind("10 knots", "40 knots", "CAR model"), tab1, tab2))

#convert numeric day to Date
tab3[,4] <- as.Date("01/01/2013", "%m/%d/%Y") + as.numeric(as.character(tab3[,4]))
tab3[,5] <- as.Date("01/01/2013", "%m/%d/%Y") + as.numeric(as.character(tab3[,5]))
tab3[,6] <- as.Date("01/01/2013", "%m/%d/%Y") + as.numeric(as.character(tab3[,6]))
tab3[,7] <- as.Date("01/01/2013", "%m/%d/%Y") + as.numeric(as.character(tab3[,7]))

# Convert these to text day of year
tab3[,4] <- paste(mday(tab3[,4]), month(tab3[,4], label = T), sep = "-")
tab3[,5] <- paste(mday(tab3[,5]), month(tab3[,5], label = T), sep = "-")
tab3[,6] <- paste(mday(tab3[,6]), month(tab3[,6], label = T), sep = "-")
tab3[,7] <- paste(mday(tab3[,7]), month(tab3[,7], label = T), sep = "-")

names(tab3) <- c("Model", "DIC", "pD", "5%", "25%", "75%", "95%")

kable(tab3)
```
  
$^1$ DIC: Deviance information criteria  
$^2$ pD: Estimate of model complexity  
$^3$ 5-95%: Estimated day of the year when $x$% of the abortions have occurred.  

**Table 2**. Expected number of abortions per month for 100 seropositive elk using different model structures. Numbers inside the brackets are the 95% credible interval. 

```{r abortions-per-month, echo=FALSE, message=FALSE}
# Calculate the probability of abortion per month
start.offset <- min(Data$CapDOY)
Day <- seq.Date(as.Date('2013/01/01') + start.offset, 
                as.Date('2013/01/01') + start.offset + D-1, by = 1)
Mo <- month(Day)

Abortion_density <- as.data.frame(cbind(Mo, t(ft_mod10k$stats[c(1,4), ]*100),
                                        ft_mod10k$mean*100,
                                        t(ft_mod40k$stats[c(1,4), ]*100), 
                                        ft_mod40k$mean*100,
                                        t(ft_icar$stats[c(1,4), ]*100),
                                        ft_icar$mean*100))

names(Abortion_density) <- c("Mo", "10k_vlo", "10k_vhi", "10k_mean",
                             "40k_vlo",  "40k_vhi", "40k_mean",
                             "icar_vlo", "icar_vhi", "icar_mean")

# expected abortion probability per month per seropositive elk
Abortion_density_mo <- aggregate(Abortion_density[,2:10], by = list (Mo), 
                                 FUN = "sum")

Table2 <- as.data.frame(round(t(as.matrix(Abortion_density_mo)), 1)[2:10,2:7])
names(Table2) <- c("Feb", "Mar", "Apr", "May", "Jun", "Jul")

Table2$Model <- row.names(Table2)
row.names(Table2) <- seq(1, dim(Table2)[1],1)
Table2 <- Table2[,c(7,1:6)]
kable(Table2)
```

Note: this table will need to be reformatted a little for the final version. 
vhi  = 97.5th percentile
vlo = 2.5th percentile
