**Table 1**. Comparison of elk abortion timing across models with different smoothing functions for the total hazard of a reproductive event. In all cases, the sub-model of the probability of an abortion relative to a live birth was a logistic regression.        

```{r Table1-comp, results='asis', echo = FALSE}
setwd("~/BitBucket/VIT/Analysis")
load('Result_icar1.RData')
load('Result_mod10k1.RData')
load('Result_mod40k1.RData')
load('VIT_Data2013_Full_POS.RData')
library(knitr)
library(lubridate)
source('ft_calc_fxn.R')
start.offset <- min(Data$CapDOY)

# Calculating summary statistics on the abortion event density for different models. 
ft_icar <- ft_calc(icarmod)
ft_icarcum <- ft_cum_calc(ft_icar$median)
ft_mod10k <- ft_calc(mod10k)
ft_mod10kcum <- ft_cum_calc(ft_mod10k$median)
ft_mod40k <- ft_calc(mod40k)
ft_mod40kcum <- ft_cum_calc(ft_mod40k$median)
ft_mod10k_5 <- start.offset + ft_mod10kcum$row5 
ft_mod40k_5 <- start.offset + ft_mod40kcum$row5 
ft_icar_5 <- start.offset + ft_icarcum$row5 
ft_mod10k_25 <- start.offset + ft_mod10kcum$row25 
ft_mod40k_25 <- start.offset + ft_mod40kcum$row25 
ft_icar_25 <- start.offset + ft_icarcum$row25 
ft_mod10k_75 <- start.offset + ft_mod10kcum$row75 
ft_mod40k_75 <- start.offset + ft_mod40kcum$row75 
ft_icar_75 <- start.offset + ft_icarcum$row75 
ft_mod10k_95 <- start.offset + ft_mod10kcum$row95 
ft_mod40k_95 <- start.offset + ft_mod40kcum$row95 
ft_icar_95 <- start.offset + ft_icarcum$row95 

# model summaries
tab1 <- round(matrix(data = c(mod10k$BUGSoutput$DIC, mod40k$BUGSoutput$DIC, icarmod$BUGSoutput$DIC, 
                        mod10k$BUGSoutput$pD, mod40k$BUGSoutput$pD, icarmod$BUGSoutput$pD), 
               nrow = 3), 1)
# Density estimates
tab2 <- matrix(data = c(ft_mod10k_5, ft_mod40k_5, ft_icar_5,  
               ft_mod10k_25, ft_mod40k_25, ft_icar_25,  
               ft_mod10k_75, ft_mod40k_75, ft_icar_75,  
               ft_mod10k_95, ft_mod40k_95, ft_icar_95), nrow = 3)
tab3 <- as.data.frame(cbind(rbind("10 knots", "40 knots", "CAR model"), tab1, tab2))

#convert numeric day to Date
tab3[,4] <- as.Date("01/01/2013", "%m/%d/%Y") + as.numeric(as.character(tab3[,4]))
tab3[,5] <- as.Date("01/01/2013", "%m/%d/%Y") + as.numeric(as.character(tab3[,5]))
tab3[,6] <- as.Date("01/01/2013", "%m/%d/%Y") + as.numeric(as.character(tab3[,6]))
tab3[,7] <- as.Date("01/01/2013", "%m/%d/%Y") + as.numeric(as.character(tab3[,7]))

# Convert these to text day of year
tab3[,4] <- paste(mday(tab3[,4]), month(tab3[,4], label = T), sep = "-")
tab3[,5] <- paste(mday(tab3[,5]), month(tab3[,5], label = T), sep = "-")
tab3[,6] <- paste(mday(tab3[,6]), month(tab3[,6], label = T), sep = "-")
tab3[,7] <- paste(mday(tab3[,7]), month(tab3[,7], label = T), sep = "-")

names(tab3) <- c("Model", "DIC", "pD", "5%", "25%", "75%", "95%")

kable(tab3, format = 'markdown')
```
  
$^1$ DIC: Deviance information criteria  
$^2$ pD: Estimate of model complexity  
$^3$ 5-95%: Estimated day of the year when $x$% of the abortions have occurred.  

```{r abortions-per-month, echo=FALSE, message=FALSE}
# Calculate the probability of abortion per month
start.offset <- min(Data$CapDOY)
Day <- seq.Date(as.Date('2013/01/01') + start.offset, 
                as.Date('2013/01/01') + start.offset + D-1, by = 1)
Mo <- month(Day)
temp <- as.data.frame(cbind(Mo, ft_mod40k$mean))
names(temp) <- c("Mo", "ab.pr")
# expected abortion probability per month per seropositive elk
x <- aggregate(temp$ab.pr, by = list (Mo), FUN = "sum")
x[,2] <- round(x[,2],3)

```