Data Preparation for the Subset of intervals 3days or less. 
========================================================

First load in the data and do some initial formating. 
```{r setup}
library(knitr)
opts_chunk$set(dev = c('png', 'pdf'), dpi = 96, fig.height = 6, fig.width = 6)
# Change the dpi to 96 if only going the html
# Change the dpi to >400 if going to a docx or pdf
```

```{r data-formatting}
setwd("~/BitBucket/VIT2014/Analysis")
rm(list = ls())
source('VITplot_interval2.r')
library(lubridate)

Data <- read.table("VIT_Data2014.txt", sep="", header=T) #load in data
# reformat some of the dates
Data$CaptureDate <- mdy(as.character(Data$CaptureDate))
Data$Start_Interval <- mdy(as.character(Data$Start_Interval))
Data$Stop_Interval <- mdy(as.character(Data$Stop_Interval))
                       
# insert death dates on mothers that died
Data$Stop_Interval[Data$VIT_Status == "Died"] <- Data$Start_Interval[Data$VIT_Status == "Died"]

# make the dates an integer for indexing purposes. 
Data$CapDOY <- yday(Data$CaptureDate) # day of the capture (1-365)
Data$StartDOY <- yday(Data$Start_Interval) # day when the VIT is first possibly out
Data$EndDOY <- yday(Data$Stop_Interval) # last day the event (birth or abortion) could have happened

Data$interval1 <- Data$StartDOY - Data$CapDOY # days from capture to the time when the VIT is first possibly out of the animal
Data$interval2 <- Data$EndDOY - Data$StartDOY # first to last day that the event could have happened. 
Data$TrustRating <- as.factor(Data$TrustRating)
head(Data)
summary(Data)
```

**MetaData**  
One row for each elk with a Vaginal Implant Transmitter (VIT).  
CaptureDate = Day the VIT was implanted  
Start_Interval = beginning of the interval over which the VIT was expelled.  
Stop_Interval = end of the interval over which the VIT was expelled.  
VIT_Status = abortion, parturition, unknown (based on site characteristics), 
  died = mother died, open = not pregnant.  
PET = flag for whether the VIT data on when it was expelled is usable.    
CowSero = brucellosis status of the mother  
DOY  = 1-365 day of the year  
VIT_Bruc = whether or not brucella was able to be cultured from the VIT or birth site. 

**TrustRating** or Data Quality flag  
1. Exact date of event known: reliable PET,direct observation or GPS-VIT utm intersection in GIS  
2. Interval reliable based on PET/flights/retrieval/GPS-VIT utm intersection in GIS  
4. Long Interval: dates based mostly on flights, deployment and recovery; not able to shorten b/c either no GPS data  
5. Interval goes from VIT deployment to retrieval with no means to shorten  
6. Unique issues, see comments. 
7. All the elk that the VIT malfunctioned, was never found, elk died, or elk wasn't pregnant  
 
The total number of elk in the initial dataset = `r nrow(Data)`.  
  
Construct some cross-tabulations of the data
```{r tabluations}
summary(Data$VIT_Status)
# Table of effort per year
table(year(Data$CaptureDate))
table(year(Data$CaptureDate), Data$VIT_Status) # most of the unknowns happened early on. 
# Table of event types by trust rating
table(Data$VIT_Status, Data$TrustRating)
# Look at the Unknowns
Data[Data$VIT_Status == "Unknown", c(1:5, 11)]
```

Remove the lost and unknown vits, non-pregnant animals.  
Also remove the intervals that are longer than 3 days. 

```{r initial-subset}
Data <- subset(Data, Data$VIT_Status != "Open" ) # remove non-pregnants
Data <- subset(Data, Data$VIT_Status != "Unknown" ) # remove unknowns
Data <- subset(Data, is.na(Data$StartDOY) != T )


# maximum possible time out
max.time <- Data$RecoveryInterval + Data$interval2

############### Subset to 3 days##################
# must be within 3 days of it coming out
Data <- subset(Data, Data$RecoveryInterval <= 3 )
# must be within 3 days of it being known in to known out 
Data <- subset(Data, Data$interval2 <= 3 )

# maximum possible time out
max.time2 <- Data$RecoveryInterval + Data$interval2

# what proportion of the records are within x days of recovery.
quantile(max.time, probs = seq(0,1,.05), na.rm = T)
quantile(max.time2, probs = seq(0,1,.05))

Data$VIT_Status <- as.factor(as.character(Data$VIT_Status)) #relevel the factor
summary(Data$VIT_Status)
table(year(Data$CaptureDate))
summary(Data)
```

Plot each individual's timeline. Grey lines are from the capture date to the start of the interval when the VIT was expelled.  Colored lines are the interval over which the VIT was expelled.  The colors indicate the type of event. 
```{r vitplot-all}
source('VITplot_interval2.r')
par(mfrow = c(1,1))
VITplot_interval2(Data, 1.5) 
```

Now just plot the positives.
```{r vitplot-pos-only}
tmp <- Data[Data$CowSero == "POS", ]
VITplot_interval2(tmp, 2)
rm(tmp)
```

Prepare the data for BUGS models
-------------------------------------------------------------------------------
Create two different datasets:  
1. Type--Dataset of only the events and what type they are.  I use this to partition the hazard of an event between abortions and live births  
2. Data--Dataset that includes a row for each non-event (capture to start date), and a row for each event

```{r}
Data$event <- 1  # does an event (abortion or birth) occur in this time interval?
Data$event[Data$VIT_Status == "Died"] <- 0 # rows that are censored by mom's death 

#### Taking out the outlier abortion to check the model
#row <- which(Data$VIT_Status == "Abortion" & Data$EndDOY >180)
#Data <- Data[-row, ]

n <- dim(Data)[1] # number of elk
Data <- Data[order(Data$Elk_ID, Data$CapDOY),] # sort it

OldData <- Data # prior to adding in stuff, save this.
# add in non-event rows for each event
j <- 1
for(i in 1:n){
  if(Data$event[i] == 1){
    # add in a row at the end
    Data[(n+j),] <- Data[i,]
    Data$event[(n+j)] <- 0        # nothing happens in this new record
    j <- j+1
  }
}

Data$left <- NA
Data$right <- NA

# for the rows where an event happens the interval is from Start to Stop
Data$left[Data$event == 1] <- Data$StartDOY[Data$event == 1] 
Data$right[Data$event == 1] <- Data$EndDOY[Data$event == 1] # ending date is one day before the event 

# for the rows where an event doesn't happen the interval is from capture to start.
Data$left[Data$event == 0] <- Data$CapDOY[Data$event == 0] 
Data$right[Data$event == 0] <- Data$StartDOY[Data$event == 0]# ending date is one day before the event 

#recode left and right to be 1 to max, so that it can be used as an index in BUGS
Data$right <- Data$right - min(Data$left) + 1
Data$left  <- Data$left - min(Data$left) + 1
Data$interval <- Data$right - Data$left

# remove rows where nothing happens between capture and start interval
Data <- subset(Data, Data$interval1 != 0) 

# subset of the data where events occur
Type <- subset(Data, Data$event == 1) # This dataset has a row per elk w/ an event
# abortions coded as a one, everything else is live birth
Type$b.type <- 0
Type$b.type[Type$VIT_Status == "Abortion"]  <- 1 
```

Declare the variables for the BUGS models 
```{r}
records <- dim(Data)[1]   # number of records
b.type <- Type$b.type     # 0 = birth, 1 = abortion
n.events <- sum(Data$event)
left  <- Data$left
right <- Data$right
event <- Data$event
noevent <- rep(NA,records)
noevent[event == 1] <- 0
noevent[event == 0] <- 1
event.day <- Type$right # the day that events occurred for 1:n.events rather than 1: records
D <- max(Data$right)      # number of days in the dataset
```

Save the RData file for the BUGs models
```{r}
rm(i,j,tmp)
save.image(file = 'VIT_Data2014_Sub3.RData')
```

Also save an RData file for dataset that is Positives only. 
```{r}
DataPOS <- subset(Data, Data$CowSero == "POS")
TypePOS <- subset(Type, Type$CowSero == "POS") 
# re-save these for the positive only dataset
records <- dim(DataPOS)[1]   # number of records
b.type <- TypePOS$b.type
#entry <- TypePOS$left - min(Type$left) + 1
n.events <- sum(DataPOS$event)
left  <- DataPOS$left
right <- DataPOS$right
event <- DataPOS$event
noevent <- rep(NA,records)
noevent[event == 1] <- 0
noevent[event == 0] <- 1
event.day <- TypePOS$right # the day that events occurred for 1:n.events rather than 1: records
D <- max(DataPOS$right)      # number of days in the dataset

save.image(file = 'VIT_Data2014_Sub3_POS.RData')
```
